Assertion Contracts

### 2024-04-04 papers/assertion-contract/assertion_contract_app/paper.tex
rewise the paper

@@

In the first case, the difficulty (\lstinline|diff|) determines the amount of computation effort needed to find a reward computation. The size of the domain here is denoted as \lstinline|n| which is one size less than the array size. Given the parameter as an array \lstinline|a|, the validator's address  \lstinline|val_addr| and a seed \lstinline|s| as input, the condition \lstinline|c| is the less than or equal comparison of two expressions, which are array elements \lstinline|a[i]| and \lstinline|a[i + 1]|, indicating that the array is not sorted. %So $\pi_{P_{i}}$ = \{\lstinline|a[i]|, \lstinline|a[i + 1]|\}. 
The condition is checked first to detect the counterexample. If not, the hash is computed to determine if it is less than the target hash. If so, a reward computation is found.

@@

%\paragraph{Sorted arrays.}{ on/off-chain assertion program for sorted arrays}
%\begin{lstlisting}[numbers=none]
%pragma solidity >=0.7.0 <0.9.0;

%/**
% * On/off-chain assertion contract 
% * to check counterexamples/computational proofs
% */
%contract Validator{

 %   /**
 %    * The difficulty for a computational proof
 %    */
 %   uint diff = 1;
 %   uint public target = 2 ** (256 - diff); 
 %
 %   /**
 %  * The result: 0 = non-award, 1 = proof, 
 %   2 = counterexample
 %   */
 %
 %   function verify_parameter(uint[] memory a, uint seed)
 %   public view returns (uint) {
 %       uint range = a.length - 1; 
 %      require(range > 0, "invalid range");
 %       uint n = seed % range;
 %       
 %       bool p = (a[n] > a[n + 1]);
 %
 %       uint result = 0; // an non-award computational proof 
 %       
 %       if (p)  
 %           result = 2; // a counterexample
 %       else 
 %           {
 %           uint current_hash = 
 %               uint (keccak256(abi.encodePacked(seed, a[n], a[n + 1])));
 %           if (current_hash <= target) 
 %               result = 1; // a computational proof      
 %       }             
 %       return result;           
 %   }
%}

%\end{lstlisting}

>>>>

An assertion in smart contract languages, such as Solidity and Michelson, is essentially predicate logic expressed as a Boolean formula computed from relational operators ($=$, $!=$, $>$, $<$, $>=$, $<=$), logical operators ($!$, $\&\&$, $\|$), and expressions. To represent the set of expressions involved in the computation of the predicate $P_a$, let $\pi_{P_{a}}$ = {$e_1$, $e_2$, \dots }. The expressions $\pi_{P_a}$ can be used to compute the hash, which involves the validator executing the condition check to find a reward computation.

@@

In the first case, the difficulty (\lstinline|diff|) determines the amount of computation effort needed to find a reward computation. The size of the domain here is denoted as \lstinline|n| which is one size less than the array size. Given the parameter as an array \lstinline|a|, the validator's address  \lstinline|val_addr| and a seed \lstinline|s| as input, the condition \lstinline|c| is the less than or equal comparison of two expressions, which are array elements \lstinline|a[i]| and \lstinline|a[i + 1]|, indicating that the array is not sorted. So $\pi_{P_{i}}$ = \{\lstinline|a[i]|, \lstinline|a[i + 1]|\}. 
The condition is checked first to detect the counterexample. If not, the hash is computed to determine if it is less than the target hash. If so, a reward computation is found.

@@
